### 2014-12-05 simulation.Rmd

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
pandoc.table(mr_compare, style="rmarkdown")
```

>>>>

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
time <- as.numeric(simseq.opt$tlen)
mr_compare <- data.frame( 
    fit=c( model@mutrates / time, model@selcoef, model@params), 
    stringsAsFactors=FALSE )
simvalues <- data.frame(
        names=c(
            mutnames(simseq.config$tip$mutpats), 
            selnames(simseq.config$tip$selpats), 
            names(simseq.config$tip$fixfn.params) ),
        simulated=unlist(c(
            simseq.config$tip$mutrates,
            simseq.config$tip$selcoef,
            simseq.config$tip$fixfn.params ) )
)
mr_compare$simulated <- simvalues$simulated[match(rownames(mr_compare),simvalues$names)]
pandoc.table(mr_compare, style="rmarkdown")
```
